### 2020-04-15 dataprep.tex
pipes into

The location references are cabinet row (0-24), column (0-7), cage
(0-3), slot (0-7), and node (0-3) with respect to the layout shown in
Figure~\ref{fig:layout}.
\begin{figure}
  \centering
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanCabinet.png}
  \end{minipage}
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanBlade.png}

@@

\fix{How does the cooling water circulate?}

>>>>

The location references are cabinet column (0-24), row (0-7), cage
(0-3), slot (0-7), and node (0-3) with respect to the layout shown in
Figure~\ref{fig:layout}.
\begin{figure}
  \centering
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanCabinet.png}
  \end{minipage}
  \begin{minipage}{0.49\columnwidth}
    \includegraphics[width=\columnwidth]{figs/TitanBlade.png}

@@

\fix{How does the coolant circulate? I notice three sets of pipes on
  each side of each row: (2 x 3) x 8 = 48 sets.}
